Cosmology with Weak Lensing photometric surveys: constraints with redshift tomography of non--Gaussian statistics

### 2016-04-15 photoz_paper/paper.tex
update figure 4
incorporated Morgan edits

\begin{abstract}
Weak Gravitational Lensing is becoming a popular technique to constrain cosmological parameters, such as the Dark Energy equation of state $w$. When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations. We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments. We find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only a few $10\%$. We also find that the addition of peak and counts to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet. We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints. We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration. 
\end{abstract}

\keywords{Weak Gravitational Lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

@@

\section{Introduction}
%
Weak Gravitational Lensing is a promising technique to probe the Large Scale Structure of the universe in which the tracers are unbiased \citep{wlreview}. This technique has the potential of improving significantly the constraints on the Dark Energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage. Cosmology inferences from Weak Lensing observations have been produced for past (CFHTLenS \citep{cfht1}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}). Because of the non-linear nature of the density fluctuations probed by Weak Lensing, cosmological information might leak from quadratic statistics (such as two point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling from cosmological parameters requires numerical simulations of cosmic shear fields. Different examples of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature (see \citep{MinkJan,PeaksJan,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} for a non comprehensive list). The constraining power of Weak Lensing power spectra with the addition of redshift tomography information have been extensively investigated in the literature (see \citep{SongKnox,FangHaiman07,Huterer2006}). In this work we concentrate on the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey. Previous work on redshift tomography with Weak Lensing Minkowski functionals is also present in the literature \citep{MinkJan}. We also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography. This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and photometric redshift systematics. We then give an overview of the parameter inferences techniques we used to forecast constraints on cosmology. We then discuss the main results of this work and present our conclusions as well as prospects for future work.

@@

\subsection{Cosmic shear simulations}
\label{sec:shearsim}
We review the procedure used for generating mock shear catalogs. We consider a fiducial flat $\Lambda$CDM universe with $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$. We examine different variations of the $\bb{p}=(\Omega_m,w,\sigma_8)$ triplet and run one $N$--body simulation for each choice of $\bb{p}$, using the public code \ttt{Gadget2} \citep{Gadget2}. The simulations have a comoving box size of $L_b=260\,{\rm Mpc}/h$ and contain $512^3$ dark matter particles, which correspond to a mass resolution of $M_p\approx 10^{10}M_{\rm sun}$ per particle. The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$. We make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to trace the deflections of light rays originating at $z=0$ through the system of lenses until $z$. To accomplish this task, we make use of the \ttt{LensTools} \citep{LensTools-ASCL,LensTools-paper} implementation of the multi--lens--plane algorithm. An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ODE up to redshift $z_s$. The Jacobian of $\pmb{\beta}(\pmb{\theta},z_s)$ is a $2\times 2$ matrix that contains information about the cosmic shear field at $\pmb{\theta}$ integrated along the line of sight. 
%
\begin{equation}
\label{meth:sheareqn}
\frac{\partial\beta_i(\pmb{\theta},z_s)}{\partial \theta_j} = 
\begin{pmatrix}
1-\kappa(\pmb{\theta})-\gamma^1(\pmb{\theta}) & -\gamma^2(\pmb{\theta}) \\
-\gamma^2(\pmb{\theta}) & 1-\kappa(\pmb{\theta})+\gamma^1(\pmb{\theta})\\
\end{pmatrix}
\end{equation}  
%
The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from Large Scale Structure, assuming the non lensed shape is a circle. 
We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$. The galaxies have a distribution in redshift which mimics the one expected in the LSST survey
\begin{equation}
\label{meth:galdistr}
n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right)
\end{equation}  
%
with $z_0=0.3$ and $n_0$ a normalization constant fixed so that $n(z)$ integrates to the total number of galaxies $N_g$. The galaxies have a maximum redshift $z_{\rm max}=3$. For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$. Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the Large Scale Structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}. We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}_g\}$. These shear realization cover the total survey area of LSST 10 times.
We repeat the above procedure for $P=100$ different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme. The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}. The parameter space sampling we adopted for our simulations is shown in Figure \ref{fig:simdesign}

\begin{figure*}
\includegraphics[scale=0.35]{Figures/design.eps}
\caption{Parameter space sampling chosen for our simulations. We show both the sampling in the $(\Omega_m,w)$ (left), $(\Omega_m,\sigma_8)$ (center) and $(\sigma_8,w)$ (right) slices of the parameter space. The fiducial cosmology has been marked in red.}
\label{fig:simdesign}
\end{figure*}
%
For each of the parameter choices in Figure \ref{fig:simdesign}, the $N$--body initial conditions are generated using the same random seed. In addition to these simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$. In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number $N_r=16000$ of pseudo--independent catalog realizations is produced. This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct mock observations that are independent on the simulations on which the cosmological forward model is trained. For the fiducial dataset we chose to base the shear randomization procedure on 5 independent $N$--body simulations to ensure the independence of the $N_r$ realizations for the purpose of estimating covariance matrices. \citep{PetriVariance} recently showed that, even with only one $N$--body simulation a few $10^4$ independent realizations can be produced.

@@

The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to Large Scale Structure if the non--lensed galaxy shape is a circle. If this assumption is relaxed, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ can be modeled as a cosmic shear term plus a noise term \citep{wlreview}
\begin{equation}
\pmb{\epsilon}_{\rm m} = \pmb{\gamma} + \pmb{\epsilon}_{\rm n}
\end{equation} 
%
where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z_s)=0.15+0.035z_s$. This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$. 
We add independent random realizations of the shape noise $\pmb{\gamma}_{\rm n}$ to each of the $N_r$ shear catalogs. Each shape noise realization is generated with a different random seed. The same random seeds are used to generate shape noise catalogs across simulations with different cosmological parameters $\{\bb{p}_i\}$.

@@

We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
\begin{equation}
\label{meth:photoz-correction}
z_p(z_s) = z_s + b_{\rm ph}(z_s) + \sigma_{\rm ph}(z_s)\mathcal{N}(0,1)   
\end{equation}
%
where $\mathcal{N}(0,1)$ is the standard normal distribution. We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins $\bar{z}_b$, $b=1...5$. Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}). We chose the photo-$z$ bias and variance functions in equation (\ref{meth:photoz-correction}) to be the science requirements contained in the LSST Science Book \citep{LSSTSciBook}, namely $b(z_s)=0.003(1+z_s)$ and $\sigma(z_s)=0.02(1+z_s)$.

@@

We generate mock observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$. In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a mock observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.

@@

\subsection{Convergence reconstruction}
In this paragraph we describe the procedure we used to construct convergence maps $\kappa$ from the simulated shear catalogs $\pmb{\gamma}$. We consider a two dimensional square pixel grid of area $\theta_{\rm FOV}^2$ and with 512 pixel per side. This correspond to a linear pixel resolution of $0.5 \rm{arcmin}$. We assign a shear value $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$ to each pixel $\pmb{\theta}_p$ according to the following procedure
\begin{equation}
\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b) = \frac{\sum_{g=1}^{N_g}\pmb{\gamma}(\pmb{\theta}_g,z_g)W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}{\sum_{g=1}^{N_g}W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}
\end{equation}   
%
We chose a top--hat window function
\begin{equation}
W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b) = 
\begin{cases}
1 \,\,\,\,{\rm if}\,\,\,\, \pmb{\theta}_g\in\pmb{\theta}_p,z_g\in\bar{z}_b \\
0 \,\,\,\,{\rm otherwise}
\end{cases}
\end{equation} 
%
The convergence $\kappa(\pmb{\theta}_p)$ can be reconstructed from the $E$--mode of the shear field, which is evaluated from the Fourier Transform of the pixelized shear $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$
\begin{equation}
\label{meth:psdefinition}
\tilde\kappa(\pmb{\ell},\bar{z}_b) = \left(\frac{\tilde{\gamma}^1(\pmb{\ell},\bar{z}_b)(\ell_x^2-\ell_y^2)+2\ell_x\ell_y\tilde{\gamma}^2(\pmb{\ell},\bar{z}_b)}{\ell_x^2+\ell_y^2}\right) e^{-\frac{\ell^2\theta_G^2}{2}}
\end{equation}
%
We chose the Gaussian filter smoothing scale $\theta_G=0.5\,{\rm arcmin}$ to correspond to the linear pixel resolution. Inverting the Fourier Transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$. We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the mock observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and mock convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.

We measure a variety of summary statistics from the pixelized convergence maps, which will then be used to forecast parameter constraints and biases. We consider three kinds of summary statistics, namely the $\kappa$ tomographic power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, the tomographic peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and a set of $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$. The tomographic power spectrum is defined as 
\begin{equation}
\langle\tilde{\kappa}(\pmb{\ell},\bar{z}_b)\tilde{\kappa}(\pmb{\ell}',\bar{z}_{b'})\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})
\end{equation}
%
Because the $\kappa$ field is statistically isotropical, the expectation value $\langle\rangle$, for each realization $r$, is taken over all the modes $\pmb{\ell}$ which have the same magnitude $\ell=\vert\pmb{\ell}\vert$. The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the $\kappa$ local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the $\kappa$ standard deviation over pixels. The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows (see \citep{Matsubara10,Munshi12,MinkPetri}) 
%
\begin{equation}
\label{meth:momdef}
\begin{matrix}
\pmb{\mu} = (\pmb{\mu}_2,\pmb{\mu}_3,\pmb{\mu}_4) \\ \\
\pmb{\mu}_2 = (\langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle) \\ \\
\pmb{\mu}_3 = (\langle\kappa^3\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle,\langle\kappa^2\nabla^2\kappa\rangle) \\ \\
\pmb{\mu}_4 = (\langle\kappa^4\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c)
\end{matrix}
\end{equation}
%
In equation (\ref{meth:momdef}) the gradients $\nabla$ are evaluated using finite differences between $\kappa$ values at neighboring pixels and the expectation values $\langle\rangle$ for each realization $r$ are taken over the $512^2$ pixels in the map. The subscript $c$ indicates that we consider only the connected parts of the quartic $\kappa$ moments. In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity. In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from mock observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.

@@

The $1\sigma$ square parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$. The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText} for a possible reference).

>>>>

\begin{abstract}
Weak gravitational lensing is becoming a mature technique to constrain cosmological parameters, such as the dark energy equation of state $w$. When analyzing galaxy surveys, redshift information has proven to be a valuable addition to angular shear correlations. We forecast parameter constraints on the triplet $(\Omega_m,w,\sigma_8)$ for a LSST like galaxy photometric survey, using tomography of the shear-shear power spectrum, convergence peak counts and higher convergence moments. We find that the addition of peak counts and moments to the power spectrum can significantly improve the constraints on the $(\Omega_m,w)$ doublet. We also find that most the cosmological information is contained in the highest redshift galaxies, with redshift tomography further improving the $w$ constraints by only 15\% to 30\%. We evaluate the effect of uncorrected photometric redshift systematics on parameter constraints. We find that different statistics lead to different bias directions in parameter space, leaving a window open for self--calibration. 
\end{abstract}

\keywords{Weak gravitational lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

@@

\section{Introduction}
%
Weak gravitational lensing is a promising technique to probe the large scale structure of the universe in which the tracers are unbiased \citep{wlreview}. This technique has the potential of improving significantly the constraints on the dark energy equation of state $w$ because it is most sensitive to the matter density fluctuations at the non--linear stage. Cosmology inferences from Weak Lensing observations have been produced for past (CFHTLenS \citep{cfht1}) and current (DES \citep{DES}) surveys, and are being planned for future experiments as well (LSST \citep{LSST}, WFIRST \citep{WFIRST}, Euclid \citep{Euclid}). Because of the non-linear nature of the density fluctuations probed by Weak Lensing, cosmological information might leak from quadratic statistics (such as two point functions and power spectra) into more complicated non-Gaussian statistics, for which forward modeling from cosmological parameters requires numerical simulations of cosmic shear fields. Different examples of these non-Gaussian statistics, and their cosmological information content, have been investigated extensively in the literature (see \citep{MinkJan,PeaksJan,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} for a non comprehensive list). The constraining power of Weak Lensing power spectra with the addition of redshift tomography information have been extensively investigated in the literature (see \citep{SongKnox,FangHaiman07,Huterer2006}). In this work we concentrate on the constraining power of a subset of these non-Gaussian statistics combined with redshift tomography in a LSST-like survey. Previous work on redshift tomography with Weak Lensing Minkowski functionals is also present in the literature \citep{MinkJan}. We also investigate the effects of uncorrected photometric redshift systematics on parameter constraints when using redshift tomography. This work is organized as follows: we give an outline of the shear simulations we use in this work, followed by descriptions of the convergence reconstruction procedure and forward modeling of galaxy shape and photometric redshift systematics. We then give an overview of the parameter inferences techniques we used to forecast constraints on cosmology. We then discuss the main results of this work and present our conclusions as well as prospects for future work.

@@

\subsection{Cosmic shear simulations}
\label{sec:shearsim}
We review the procedure used for generating simulated shear catalogs. We consider a fiducial flat $\Lambda$CDM universe with $(h,\Omega_m,\Omega_\Lambda,\Omega_b,w,\sigma_8,n_s)=(0.72,0.26,0.74,0.046,-1,0.8,0.96)$. We examine different variations of the $\bb{p}=(\Omega_m,w,\sigma_8)$ triplet and run one $N$--body simulation for each choice of $\bb{p}$, using the public code \ttt{Gadget2} \citep{Gadget2}. The simulations have a comoving box size of $L_b=260\,{\rm Mpc}/h$ and contain $512^3$ dark matter particles, which correspond to a mass resolution of $M_p\approx 10^{10}M_{\rm sun}$ per particle. The three dimensional outputs of the $N$--body simulations are sliced in sequences of two dimensional lenses $120 \,{\rm Mpc}$ thick, which are lined up perpendicular to the line of sight between the observer on Earth and a source at redshift $z_s$. We make use of the multi--lens--plane algorithm \citep{RayTracingJain,RayTracingHartlap} to trace the deflections of light rays originating at $z=0$ through the system of lenses until $z$. To accomplish this task, we make use of the \ttt{LensTools} \citep{LensTools-ASCL,LensTools-paper} implementation of the multi--lens--plane algorithm. An observed galaxy position $\pmb{\theta}$ on the sky today corresponds to a real galaxy angular position $\pmb{\beta}(\pmb{\theta},z_s)$, which can be calculated using the \ttt{LensTools} pipeline by solving the lensing ordinary differential equations up to redshift $z_s$. The Jacobian of $\pmb{\beta}(\pmb{\theta},z_s)$ is a $2\times 2$ matrix that contains information about the cosmic shear field at $\pmb{\theta}$ integrated along the line of sight. 
%
\begin{equation}
\label{meth:sheareqn}
\frac{\partial\beta_i(\pmb{\theta},z_s)}{\partial \theta_j} = 
\begin{pmatrix}
1-\kappa(\pmb{\theta})-\gamma^1(\pmb{\theta}) & -\gamma^2(\pmb{\theta}) \\
-\gamma^2(\pmb{\theta}) & 1-\kappa(\pmb{\theta})+\gamma^1(\pmb{\theta})\\
\end{pmatrix}
\end{equation}  
%
The quantities that appear in equation (\ref{meth:sheareqn}) are the convergence $\kappa$, which is the source magnification due to lensing, and the cosmic shear $\pmb{\gamma}$, which is a measurement of the source ellipticity due to lensing from large scale structure, assuming the non lensed shape is a circle. 
We simulate $N_g = 10^6$ random galaxy positions $\{\pmb{\theta}_g\}$ distributed uniformly in a field of view of size $\theta_{\rm FOV}^2=(3.5{\rm deg})^2$, which correspond to a galaxy angular density of $n_g=22\,\rm{arcmin}^{-2}$. The galaxies have a distribution in redshift which mimics the one expected in the LSST survey
\begin{equation}
\label{meth:galdistr}
n(z) = n_0\left(\frac{z}{z_0}\right)^2\exp\left(-\frac{z}{z_0}\right)
\end{equation}  
%
with $z_0=0.3$ and $n_0$ a normalization constant fixed so that $n(z)$ integrates to the total number of galaxies $N_g$. The galaxies have a maximum redshift $z_{\rm max}=3$. For each galaxy we compute the cosmic shear at $\pmb{\theta}_g$ using equation (\ref{meth:sheareqn}), producing a shear catalog $\{\pmb{\gamma}_g\}$. Different random realizations of a shear catalog $\{\pmb{\gamma}_g\}_r$ can be obtained rotating and periodically shifting the large scale structure in the $N$--body snapshots according to the procedure explained in \citep{PetriVariance}. We produce $N_r=16000$ pseudo--independent realizations of the shear catalog $\{\pmb{\gamma}_g\}$. These shear realization cover the total survey area of LSST 10 times.
We repeat the above procedure for $P=100$ different combinations of the parameter triplet $\bb{p}$, sampled according to a Latin hypercube scheme. The sampling procedure is the same described in \citep{CFHTMink,CFHTPeaks}. The parameter space sampling we adopted for our simulations is shown in Figure \ref{fig:simdesign}

\begin{figure*}
\includegraphics[scale=0.35]{Figures/design.eps}
\caption{Parameter space sampling chosen for our simulations. We show both the sampling in the $(\Omega_m,w)$ (left), $(\Omega_m,\sigma_8)$ (center) and $(\sigma_8,w)$ (right) slices of the parameter space. The fiducial cosmology has been marked in red.}
\label{fig:simdesign}
\end{figure*}
%
For each of the parameter choices in Figure \ref{fig:simdesign}, the $N$--body initial conditions are generated using the same random seed. In addition to these simulations, we produce simulated shear catalogs for a fiducial $\Lambda$CDM universe with $\bb{p}_0=(0.26,-1,0.8)$. In this case the randomization procedure is based on 5 independent $N$--body simulations, and the same number $N_r=16000$ of pseudo--independent catalog realizations is produced. This additional simulation set serves two purposes: it provides an independent dataset from which to measure covariance matrices and it provides a way to construct simulated observations that are independent of the simulations on which the cosmological forward model is trained. For the fiducial dataset we chose to base the shear randomization procedure on 5 independent $N$--body simulations to ensure the independence of the $N_r$ realizations for the purpose of estimating covariance matrices. \citep{PetriVariance} recently showed that, even with only one $N$--body simulation a few $10^4$ independent realizations can be produced.

@@

The measured galaxy ellipticity $\pmb{\epsilon}$ is an estimate of the cosmic shear $\pmb{\gamma}$ due to large scale structure if the non--lensed galaxy shape is a circle. Because the galaxies have intrinsic non circular shapes, the measured galaxy ellipticity $\pmb{\epsilon}_{\rm m}$ is the sum of a cosmic shear term and the intrinsic ellipticity (galaxy shape noise) \citep{wlreview}
\begin{equation}
\pmb{\epsilon}_{\rm m} = \pmb{\gamma} + \pmb{\epsilon}_{\rm n}
\end{equation} 
%
where $\pmb{\epsilon}_{\rm n}$ is a random Gaussian variable with zero mean and redshift dependent variance $\sigma_n(z_s)=0.15+0.035z_s$. This is equivalent to say that the cosmic shear inferred from ellipticity observations $\pmb{\gamma}_{\rm m}$ can be written as the sum of the true cosmic shear plus a noise term $\pmb{\gamma}_{\rm n}$ with the same statistical properties as $\pmb{\epsilon}_{\rm n}$. 
We add independent random realizations of the shape noise $\pmb{\gamma}_{\rm n}$ to each of the $N_r$ shear catalogs. Each shape noise realization is generated with a different random seed. The same random seeds are used to generate shape noise catalogs across simulations with different cosmological parameters $\{\bb{p}_i\}$.

@@

The study of photometric redshift errors is an active subject of research, and includes investigation of techniques such as spectroscopic calibration, catastrophic errors and cross-correlation techniques that we do not explore in this work (see for example \citep{HuTomo} for a more throughout discussion). We model effect of photo-$z$ errors as a constant bias term $b_{\rm ph}(z_s)$ plus a random Gaussian component with variance $\sigma_{\rm ph}(z_s)$
\begin{equation}
\label{meth:photoz-correction}
z_p(z_s) = z_s + b_{\rm ph}(z_s) + \sigma_{\rm ph}(z_s)\mathcal{N}(0,1)   
\end{equation}
%
where $\mathcal{N}(0,1)$ is the standard normal distribution. We bin the $N_g$ galaxies in our simulated catalogs in 5 redshift bins $\bar{z}_b$, $b=1...5$. Several models have been proposed in the literature for the photometric bias $b_{\rm ph}(z_s)$ (see for example \citep{Huterer2006}) and variance $\sigma_{\rm ph}(z_s)$ (see for example \citep{LSSTSciBook}). We chose the photo-$z$ bias and variance functions in equation (\ref{meth:photoz-correction}) to be the science requirements contained in the LSST Science Book \citep{LSSTSciBook}, namely $b(z_s)=0.003(1+z_s)$ and $\sigma(z_s)=0.02(1+z_s)$.

@@

We generate simulated observations by applying an independent random realization of the photo-$z$ correction (\ref{meth:photoz-correction}) to each catalog realization in the fiducial cosmology $\bb{p}_0$ and by re--binning the galaxies according to their photometric redshifts $z_p$. In the remainder of the paper we use the following notation: we indicate a shear realization $r$ in cosmology $\bb{p}$ with shape noise added as $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$, and we indicate a simulated observation as $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$.

@@

\subsection{Convergence reconstruction}
In this section we describe the procedure we use to construct convergence maps $\kappa$ from the simulated shear catalogs $\pmb{\gamma}$. We consider a two dimensional square pixel grid of area $\theta_{\rm FOV}^2$ and with 512 pixel per side. This correspond to a linear pixel resolution of $0.5 \rm{arcmin}$. We assign a shear value $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$ to each pixel $\pmb{\theta}_p$ according to the following procedure
\begin{equation}
\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b) = \frac{\sum_{g=1}^{N_g}\pmb{\gamma}(\pmb{\theta}_g,z_g)W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}{\sum_{g=1}^{N_g}W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b)}
\end{equation}   
%
We chose a top--hat window function
\begin{equation}
W(\pmb{\theta}_g,\pmb{\theta}_p;z_g,\bar{z}_b) = 
\begin{cases}
1 \,\,\,\,{\rm if}\,\,\,\, \pmb{\theta}_g\in\pmb{\theta}_p,z_g\in\bar{z}_b \\
0 \,\,\,\,{\rm otherwise}
\end{cases}
\end{equation} 
%
The convergence $\kappa(\pmb{\theta}_p)$ can be reconstructed from the $E$--mode of the shear field, which is evaluated from the Fourier Transform of the pixelized shear $\pmb{\gamma}(\pmb{\theta}_p,\bar{z}_b)$
\begin{equation}
\label{meth:psdefinition}
\tilde\kappa(\pmb{\ell},\bar{z}_b) = \left(\frac{\tilde{\gamma}^1(\pmb{\ell},\bar{z}_b)(\ell_x^2-\ell_y^2)+2\ell_x\ell_y\tilde{\gamma}^2(\pmb{\ell},\bar{z}_b)}{\ell_x^2+\ell_y^2}\right) e^{-\frac{\ell^2\theta_G^2}{2}}
\end{equation}
%
We chose the Gaussian filter smoothing scale $\theta_G=0.5\,{\rm arcmin}$ to correspond to the linear pixel resolution. Inverting the Fourier Transform yields the pixelized map $\kappa(\pmb{\theta}_p,\bar{z}_b)$. We apply this procedure to both the shear realizations $\h{\pmb{\gamma}}_r(\pmb{\theta}_g,z_g;\bb{p})$ and the simulated observations $\h{\pmb{\gamma}}_{\rm obs}(\pmb{\theta}_g,z_g)$, yielding convergence realizations $\h{\kappa}_r(\pmb{\theta}_p,\bar{z}_b;\bb{p})$ and simulated convergence observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$.

We measure a variety of summary statistics from the pixelized convergence maps, which will then be used to forecast parameter constraints and biases. We consider three kinds of summary statistics, namely the $\kappa$ tomographic power spectrum $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, the tomographic peak counts $n_{\rm pk}(\nu,\bar{z}_b)$ and a set of $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$. The tomographic power spectrum is defined as 
\begin{equation}
\langle\tilde{\kappa}(\pmb{\ell},\bar{z}_b)\tilde{\kappa}(\pmb{\ell}',\bar{z}_{b'})\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})
\end{equation}
%
Because the $\kappa$ field is statistically isotropical, the expectation value $\langle\rangle$, for each realization $r$, is taken over all the modes $\pmb{\ell}$ which have the same magnitude $\ell=\vert\pmb{\ell}\vert$. The peak count statistic $n_{\rm pk}(\nu,\bar{z}_b)$ is defined as the number of the $\kappa$ local maxima of a certain height $\kappa_{\rm max}=\nu\sigma_0$, where $\sigma_0$ is the $\kappa$ standard deviation over pixels. The $\kappa$ moments $\pmb{\mu}(\bar{z}_b)$ are defined as follows (see \citep{Matsubara10,Munshi12,MinkPetri}) 
%
\begin{equation}
\label{meth:momdef}
\begin{matrix}
\pmb{\mu} = (\pmb{\mu}_2,\pmb{\mu}_3,\pmb{\mu}_4) \\ \\
\pmb{\mu}_2 = (\langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle) \\ \\
\pmb{\mu}_3 = (\langle\kappa^3\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle,\langle\kappa^2\nabla^2\kappa\rangle) \\ \\
\pmb{\mu}_4 = (\langle\kappa^4\rangle_c,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle_c,\langle\kappa^3\nabla^2\kappa\rangle_c,\langle\vert\nabla\kappa\vert^4\rangle_c)
\end{matrix}
\end{equation}
%
In equation (\ref{meth:momdef}) the gradients $\nabla$ are evaluated using finite differences between $\kappa$ values at neighboring pixels and the expectation values $\langle\rangle$ for each realization $r$ are taken over the $512^2$ pixels in the map. The subscript $c$ indicates that we consider only the connected parts of the quartic $\kappa$ moments. In the definition of the peak counts and convergence moments we omitted the redshift index $\bar{z}_b$ for notational simplicity. In the next paragraph we describe the statistical methods we use to infer cosmological parameter estimates $\bbh{p}$ from simulated observations $\h{\kappa}_{\rm obs}(\pmb{\theta}_p,\bar{z}_b)$ using the summary statistics $P^{\kappa\kappa}(\ell,\bar{z}_b,\bar{z}_{b'})$, $n_{\rm pk}(\nu,\bar{z}_b)$, $\pmb{\mu}(\bar{z}_b)$.

@@

The square of the $1\sigma$ parameter errors $\Delta \bbh{p}^2$ are the diagonal entries of $\bbh{\Sigma}$. The parameter covariance estimator (\ref{meth:parcovestimator}) is the same that one gets adopting a Fisher Matrix formalism for parameter forecasts (see \citep{astroMLText}).
